\begin{thebibliography}{8}
  \bibitem{research_camera}
  Arai, H., Ito, N., Taniguti, N.: Image processing techniques for capturing
  crowds at a macroscopic level - estimating the number of people based on
  geometric models of people and crowds and its applications. Tech. Rep.~13,
  NTT Media Intelligence Laboratory, NTT Media Intelligence Laboratory, NTT
  Media Intelligence Laboratory (jan 2014)

  \bibitem{kajima}
  Corporation, K.: Smart buildings support workers' health behaviors.
  "\url{https://www.kajima.co.jp/news/press/202107/6a1-j.htm}"

  \bibitem{elenavi}
  Corporation, M.E.: Solving elevator congestion with ele-navi.
  "\url{https://www.mitsubishielectric.co.jp/elevator/nayami/002/}"

  \bibitem{cocoa_ble}
  Google: Contact tracing - bluetooth specification v1.1.
  "\url{https://blog.google/documents/58/Contact\_Tracing\_-\_Bluetooth\_Specification\_v1.1\_RYGZbKW.pdf}"

  \bibitem{ministry}
  Japan, P.M.O.O.: Prime minister's residence.
  "\url{https://www.kantei.go.jp/jp/content/000062771.pdf}"

  \bibitem{kanamitu-2021-dicomo}
  Kanemitu, Y., TAYA, E., Tachibana, K., Nakamura, Y., Matuda, Y., Suwa, H.,
  Yasumoto, K.: Estimating congestion on a bus route using ble. In: Information
  Processing Society of Japan DICOMO Symposium (2021)

  \bibitem{komai2016beacon}
  Komai, K., Fujimoto, M., Arakawa, Y., Suwa, H., Kashimoto, Y., Yasumoto, K.:
  Beacon-based multi-person activity monitoring system for day care center. In:
  2016 IEEE International Conference on Pervasive Computing and Communication
  Workshops (PerCom Workshops). pp.~1--6. IEEE (2016)

  \bibitem{komai2016elderly}
  Komai, K., Fujimoto, M., Arakawa, Y., Suwa, H., Kashimoto, Y., Yasumoto, K.:
  Elderly person monitoring in day care center using bluetooth low energy. In:
  2016 10th International Symposium on Medical Information and Communication
  Technology (ISMICT). pp.~1--5. IEEE (2016)

  \bibitem{ipsj-taikai-2020-matsumoto}
  Matumoto, T., Takahashi, R., Ishida, S., Arakawa, Y.: Initial evaluation of
  device-free indoor congestion estimation using wireless lan. In: The 82nd
  National Convention of Information Processing Society of Japan (2020)

  \bibitem{nakamura2021iot}
  Nakamura, Y., Matsuda, Y.: Iot nudge: Iot data-driven nudging for health
  behavior change. In: Adjunct Proceedings of the 2021 ACM International Joint
  Conference on Pervasive and Ubiquitous Computing and Proceedings of the 2021
  ACM International Symposium on Wearable Computers. pp. 51--53 (2021)

  \bibitem{misc/26987957}
  Suzuki, Y., Manato, M., Yoshino, K., Hidaka, M., Mai, N.Q., Nagano, K.,
  Nakamura, Y., Otubo, A., Tanaka, S., Yasumoto, K., Nakamura, T.: Construction
  of iot2h tourism information application for kyoto inbound tourism. The 11th
  Forum on Data Engineering and Information Management (DEIM2019)  (3 2019)

  \bibitem{research_elevator_log}
  Taguchi, H., Suzuki, N., Shikai, M.: Estimating passenger queue length based on
  elevator control log. In: IEICE Conferences Archives. The Institute of
  Electronics, Information and Communication Engineers (2015)

  \bibitem{research_itocon}
  Takahashi, R., Hayashi, K., Mitsukude, Y., Ninomata, M., Inoue, S., Matsuo, S.,
  Ishida, S., Arakawa, Y., Takano, S.: Bus stop congestion visualization system
  itocon. In: Proceedings of the 28th Workshop on Multimedia Communication and
  Distributed Processing. pp. 227--230 (nov 2020)

  \bibitem{research_elevator_camera}
  Uchidate, H., Inoda, R., Tsuji, T., Abe, S.: Counting people and recognition of
  wheelchairs at elevator lobby by real-time image processing. IEEJ
  Transactions D (Journal of Industrial Application Division)  \textbf{129}(6),
  578--584 (2009)

  % MARK: don't show footnote
  \thispagestyle{kisuu}

  \bibitem{umeki2018real}
  Umeki, K., Nakamura, Y., Fujimoto, M., Arakawa, Y., Yasumoto, K.: Real-time
  congestion estimation in sightseeing spots with ble devices. In: 2018 IEEE
  International Conference on Pervasive Computing and Communications Workshops
  (PerCom Workshops). pp. 430--432. IEEE (2018)
\end{thebibliography}
